---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

This is a package built for STAT545 homework08. It contains several functions mainly used to deal with factors. Here is an example of one of the function `fbind`
```{r}
library(MaryFactors)
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])
```

##Function `fbind`
###Description
This function conbines levels of two vectors. Numeric vectors will be treated as factors

###Example
```
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])

a <- c(1, 2)
b <- c('a', 'b')
fbind(a, b)

#Cannot accept weird input
b <- as.data.frame(b)
fbind(a, b)
```

##Function `freq_out`
###Description
This function makes a frequency table for a factor.

###Examples
```
freq_out(iris$Species)

#Does not accept objects other than factors
a <- c(1:10)
freq_out(a)
```

##Function `detect_char`
###Description
This function tires to detect if a variable could be of class character. It takes in a vector:

* If it's numeric, print message "This is a numeric vector"
* If it's character, print message "This is already a character vector"
* If it's factor, check if number of distinct values equals length. If so, print a message informing the user that this vector could be of class character
  + In addition, if it's suspected to be character and the argument `convert` is set to be `TRUE`, then return a the vector with its class redefined to be character

###Examples
```
x <- c(1, 2, 3)
detect_char(x)

x <- c("This", "is", "actually", "a", "sentence")
detect_char(x)

x <- as.factor(x)
class(x)
detect_char(x)
x <- detect_char(x, convert = T)
x
class(x)

#Cannot accept weird input
x <- as.data.frame(x)
detect_char(x)
```

##Fucntion `desc_reorder`
###Description
This function reorders factor levels according to the descending order of the provided corresponding numeric variable.

###Examples
```
x <- factor(c('a', 'b', 'c', 'd'))
y <- c(2, 1, 4, 3)
levels(x)
x <- desc_reorder(x, y)
levels(x)

boxplot(Sepal.Width ~ Species, data = iris)
boxplot(Sepal.Width ~ desc_reorder(Species, Sepal.Width), data = iris)

#The first argument must be factor and the second must be numeric
x <- c(2, 1, 4, 3)
y <- factor(c('a', 'b', 'c', 'd'))
desc_reorder(x, y)
x <- as.factor(x)
desc_reorder(x, y)
```
